False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-07-22 ms.tex
more writing

%% This is emulateapj reformatting of the AASTEX sample document
%%
\documentclass[preprint2]{aastex}
%\documentclass[iop]{emulateapj}

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}

@@

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI) from the Q1-Q16 catalog release.
Out of \ncalc\ KOIs, we determine that \nval\ have probabilities
$<$1\% to be astrophysical false positives, and thus may be considered
validated planets.  \nvalnew\ of these have not yet been validated or
confirmed by other methods.  In addition, we identify \nfp\ KOIs
likely to be false positives ($>$90\% probability), \nfpnew\ of which
have not yet been identified as such. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple.  These calculations
use \vespa, a publicly available Python package able to be easily
applied to any transiting exoplanet candidate.
\end{abstract}

@@

\section{Introduction}

@@

The new method now used by \vespa\ uses the \isochrones\ Python module
\citep{isochrones} to fold in observational constraints on the host
star.  At its core, \isochrones\ performs 3-D linear interpolation in
mass--[Fe/H]--age parameter space for a given stellar model grid.
This method of stellar modeling for FPP calculation debuted in
\citet{Montet:2015} and is explained there in more detail.  Instead of
randomly generating stars (or binary or triple systems of stars) from
a predefined distribution and culling them to agree with observed
colors, \emph{all} available constraints on the target star are used
to condition a direct fit of either a single--, binary--, or
triple--star model to the Dartmouth grid of stellar models.  This fit
is done using \texttt{MultiNest} \citep{Feroz:2009, Feroz:2011,
  Feroz:2013}, via the \texttt{PyMultiNest} wrapper
\citep{Buchner:2014}.  Monte Carlo samples of stellar properties for
the population simulations are then drawn directly from these
posterior samples.

@@

The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
regardless of classification as CONFIRMED, CANDIDATE, or
FALSE POSITIVE.  As such, we begin with a list of
\ntotal\ \acp{koi} from the cumulative table at the \ac{nexsci}
Exoplanet Archive.  However, for various reasons, the ancillary data
and constraints that we describe below are not available for every
\ac{koi}, and so in the end we present \ac{fpp} results for
\ncalc\ \acp{koi}.

@@

>>>>

%% This is emulateapj reformatting of the AASTEX sample document
%%
%\documentclass[preprint2]{aastex}
\documentclass{emulateapj}

@@

@@

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every \ac{koi}.
Out of \ncalc\ \acp{koi}, we determine that \nval\ have probabilities
$<$1\% to be astrophysical false positives, and thus may be considered
validated planets.  \nvalnew\ of these have not yet been validated or
confirmed by other methods.  In addition, we identify \nfp\ KOIs
likely to be false positives ($>$90\% probability), \nfpnew\ of which
have not yet been identified as such. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple.  These calculations
use \vespa, a publicly available Python package able to be easily
applied to any transiting exoplanet candidate.
\end{abstract}

@@

\section{Introduction}
\acresetall

@@

The new method now used by \vespa\ uses the \isochrones\ Python module
\citep{isochrones} to fold in observational constraints on the host
star.  At its core, \isochrones\ performs 3-D linear interpolation in
mass--[Fe/H]--age parameter space for a given stellar model grid.
This method of stellar modeling for FPP calculation debuted in
\citet{Montet:2015} and is explained there in more detail.  Instead of
randomly generating stars (or binary or triple systems of stars) from
a predefined distribution and culling them to agree with observed
colors, \emph{all} available constraints on the target star are used
to condition a direct fit of either a single--, binary--, or
triple--star model to the Dartmouth grid of stellar models
\citep{Dotter:2008, Feiden:2011}.  This fit is done using
\texttt{MultiNest} \citep{Feroz:2009, Feroz:2011, Feroz:2013}, via the
\texttt{PyMultiNest} wrapper \citep{Buchner:2014}.  Monte Carlo
samples of stellar properties for the population simulations are then
drawn directly from these posterior samples.

@@

The goal of this work is to calculate the \ac{fpp} for every \ac{koi},
regardless of classification as CONFIRMED, CANDIDATE, or FALSE
POSITIVE.  As such, we begin with a list of \ntotal\ \acp{koi} from
the cumulative table at the \ac{nexsci} Exoplanet Archive.  We then
gather ancillary data and constraints from various sources (described
below) in order to enable the \vespa\ calculation. For various
reasons, the data are not available for every \ac{koi}, and so in the
end we present \ac{fpp} results for \ncalc\ \acp{koi}.

For each \ac{koi} we obtain the following data:
\begin{enumerate}
\item The RA/Dec coordinates of each star from the \ac{kic}.
\item $grizJHK$ photometry from the \ac{kic}, with $griz$ bands
  corrected to the \ac{sdss} photometric scale according to
  \citet{Pinsonneault:2012}.
\item Stellar $T_\mathrm{eff}$, [Fe/H], and $\log g$ values and
  uncertainties from the \citet{Huber:2014} stellar properties
  catalog, if the provenance of these values is from spectroscopy or
  asteroseismology.
\item Detrended \kepler\ photometry used for the \ac{mcmc} modeling of
  \citet{Rowe:2015}, along with information about individually fitted
  transit times, where available.
\item Best-fit $R_p/R_\star$ from the \citet{Rowe:2015} MCMC analysis.
\item Centroid uncertainty information from the \ac{nexsci} Exoplanet
  Archive: we assume that the allowed ``exclusion'' radius for a blend
  scenario is 3$\times$ the uncertainty in the fitted centroid
  position (the \verb|koi_dicco_msky_err| column in the Archive
  table).  We floor this value at 0\farcs5, to prevent unrealistically
  small exclusion radii.
\item The maximum secondary eclipse depth allowed by the
  \kepler\ photometry.  This quantity is obtained from vetting
  metrics produced internally by the \kepler\ Science Office.  When
  these metrics are not available for a particular \ac{koi}, we
  default to 10$\times$ the uncertainty in the \kepler\ pipeline
  measured transit depth (\verb|koi_depth_err1|).

\end{enumerate}

@@

\acrodef{fpp}[FPP]{false positive probability}
\acrodef{koi}[KOI]{\kepler\ Object of Interest}
\acrodefplural{koi}[KOIs]{\kepler\ Objects of Interest}
\acrodef{nexsci}[NExScI]{NASA Exoplanet Science Institute}
\acrodef{mcmc}[MCMC]{Markov Chain Monte Carlo}
\acrodef{trilegal}[TRILEGAL]{TRIdimensional modeL of thE GALaxy}
\acrodef{kic}[KIC]{Kepler Input Catalog}
\acrodef{sdss}[SDSS]{Sloan Digital Sky Survey}
